### 2019-12-28 defesa/tex/chapter/introducao.tex
wip

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \citeonline{church:1974}.
In this first study, the author defined the problem on graphs with the demand being a subset of the graph's vertices. The objective was to maximize the coverage of the demand set by choosing the location of a given facility set on the graph.
Every facility had a given coverage radius, which meant that after it was placed on the graph, every vertex within that radius would be considered covered.

>>>>

The second type of covering problems arose from the fact that covering almost all the demand set can be a lot cheaper than having to cover it all \cite{garcia}. This second type is known as \sigla{\MCLP}{Maximal Covering Location Problem} and was introduced in \citeonline{church:1974}.
In this first study, the author defined the problem on graphs, and the objective was to maximize the coverage of a demand set, which was a subset of the graph's vertices, by choosing the location of a facility set, which covered any vertex within a given coverage radius.

### 2019-12-28 defesa/tex/chapter/pmclp.tex
wip

In this chapter, the classical version of PMCLP using disks will be defined and a version of the method will be proposed with the intention of later being used to solve the axis-parallel ellipses version of PMCLP. Throughout the course of this work, the maximal covering by disks problem is going to be referred to as $MCD(\Pp,m)$, where $\Pp$ is a set of points and $m$ is the number of unit disks.

@@

    \caption{The intersections list of a disk with three other disks.}
    \input{tex/figures/fig:array_disks.tex}
    \fautor
    \label{fig:array_disks}
\end{figure}

>>>>

In this chapter, we introduce the classical version of PMCLP using radius one disks, we refer to this problem as \sigla{MCD}{Maximum Covering by Disks}. We also propose a method for it intending to adapt it for the elliptical PMCLP introduced next chapter.

\section{Definition}

An instance of MCD is given by a set of $n$ demand points $\Pp:=\{p_1, \dots, p_n\}$, with $p_j\in\R^2$; and a set of $m$ unit disks $\D:=\{D_1, \dots, D_m\}$, which represent the facilities and are used to cover the demand set.

A solution for an instance of MCD chooses the location of the $m$ disks in $\D$. Formally, a solution is given by $Q:=(q_1, \dots, q_m)$, with $q_j\in\R^2$.

Let $D\in \D$ and $q\in\R^2$, then we denote $D(q)$ as disk $D$ centered at $q$. Therefore, $\Pp \cap D(q)$ denotes the set of points from $\Pp$ covered by $D$.

Given an instance of MCD, a solution for it is defined by the cen as .

@@

    \caption{The intersections list of a disk with three other disks.}
    \input{tex/figures/array_disks.tex}
    \fautor
    \label{fig:array_disks}
\end{figure}
